Group 1: Predicting the Outcomes of Tennis Tournaments

### 2019-12-12 Group1Prez.Rmd
Final Prez

```{r,echo=FALSE, fig.align='center'}
include_graphics("Serena.png")
```

@@

ggplot(data.frame(T2)) +
  geom_col(aes(x=Var1, y=Freq)) +
  xlab("Players") +
  ylab("Number of Times Won") +
  ggtitle("Which Player Won the Tournament?",
          subtitle = "2002 Men's US Open")

@@

```{r,echo=FALSE, fig.align='center'}
include_graphics("Pete.png")
```

@@

ggplot(data.frame(T3)) +
  geom_col(aes(x=Var1, y=Freq)) +
  xlab('Players') +
  ylab('Number of Times Won') +
  ggtitle('Which Player Won the Tournament?',
          subtitle = "2002 Women's Wimbledon")
```

@@

```{r, fig.align='center'}
include_graphics('Serena2.png')
```

@@

mWim02$pTC <- as.numeric(pTC(pRally[1], pRally[2], pRally[3], pRally[4], 2))

@@

ggplot(data.frame(T4)) +
  geom_col(aes(x=Var1, y=Freq)) +
  xlab('Players') +
  ylab('Number of Times Won') +
  ggtitle('Which Player Won the Tournament?',
          subtitle = "2002 Men's Wimbledon")
```

@@

```{r, fig.align='center'}
include_graphics('Hewitt.png')
```

@@

ggplot(data.frame(T4)) +
  geom_col(aes(x=Var1, y=Freq)) +
  xlab('Players') +
  ylab('Number of Times Won') +
  ggtitle('Which Player Won the Tournament?',
          subtitle = "2019 Women's Wimbledon")
```

@@

```{r,echo=FALSE, fig.align='center'}
include_graphics("Simona.png")
```

@@

mWim19$pTC <- as.numeric(pTC(pRally[1], pRally[2], pRally[3], pRally[4], 2))

@@

ggplot(data.frame(T5)) +
  geom_col(aes(x=Var1, y=Freq)) +
  xlab('Players') +
  ylab('Number of Times Won') +
  ggtitle('Which Player Won the Tournament?',
          subtitle = "2002 Men's Wimbledon")
```

@@

```{r,echo=FALSE, fig.align='center'}
include_graphics("Novak.png")
```

>>>>

\centerline{\includegraphics[height=2in]{Serena.png}}

@@

ggplot(data.frame(T2)) +
  geom_col(aes(x=Var1, y=Freq/2000)) +
  xlab("Players") +
  ylab("Proportion of Times Won") +
  ggtitle("Which Player Won the Tournament?",
          subtitle = "2002 Men's US Open")

@@

\centerline{\includegraphics[height=2in]{Pete.png}}

@@

ggplot(data.frame(T3)) +
  geom_col(aes(x=Var1, y=Freq/2000)) +
  xlab('Players') +
  ylab('Proportion of Times Won') +
  ggtitle('Which Player Won the Tournament?',
          subtitle = "2002 Women's Wimbledon")
```

@@

\centerline{\includegraphics[height=2in]{Serena2.png}}

@@

mWim02$pTC <- as.numeric(pTC(pRally[1], pRally[2], pRally[3], pRally[4], 3))

@@

ggplot(data.frame(T4)) +
  geom_col(aes(x=Var1, y=Freq/2000)) +
  xlab('Players') +
  ylab('Proportion of Times Won') +
  ggtitle('Which Player Won the Tournament?',
          subtitle = "2002 Men's Wimbledon")
```

@@

\centerline{\includegraphics[height=2in]{Hewitt.png}}

@@

ggplot(data.frame(T4)) +
  geom_col(aes(x=Var1, y=Freq/2000)) +
  xlab('Players') +
  ylab('Proportion of Times Won') +
  ggtitle('Which Player Won the Tournament?',
          subtitle = "2019 Women's Wimbledon")
```

@@

\centerline{\includegraphics[height=2in]{Simona.png}}

@@

mWim19$pTC <- as.numeric(pTC(pRally[1], pRally[2], pRally[3], pRally[4], 3))

@@

ggplot(data.frame(T5)) +
  geom_col(aes(x=Var1, y=Freq/2000)) +
  xlab('Players') +
  ylab('Proportion of Times Won') +
  ggtitle('Which Player Won the Tournament?',
          subtitle = "2002 Men's Wimbledon")
```

@@

\centerline{\includegraphics[height=2in]{Novak.png}}
